Homicide Increases in the COVID-19 Era

### 2025-03-07 Draft3.qmd
Added background map to Plot 1

```{r, echo=FALSE}

@@

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
la_shape <- read_sf(dsn = "0_Data/Raw_Data/Cities_and_Communities", layer = "Cities_and_Communities")

la_shape <- st_transform(la_shape, crs = 4326)

cali <- read_sf(dsn = "0_Data/Raw_Data/ca_counties", layer = "ca_counties")

cali <- st_transform(cali, crs = 4326)

@@

plot(la_shape$geometry, lwd=.5, add=TRUE)

plot(cali$geometry, add = TRUE, lwd=.5)
